Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-16 Manuscript_draft/Text.Rmd
adding to results pollen ratios

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented for all the species in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.

[Add values of pollen counted](Jose)

The grouped effect size of the nine donors per species differed across species and families (see **Figure 2**). Interestingly, despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**). Just for four species out of ten, just one donor in each did not overlap the confidence intervals with other donors. Therefore, none of the donors had a clear stronger or weaker effect across species. When the donors were grouped by family we found a similar effect too, just for *S. lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**). In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production. However, for just one species (*S. alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production. For two Solanaceae species *S. melongena* and *C. annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.

@@

>>>>

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented for all the species in **Figure 1** (see **Appendix 1** for table with values). Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Brassicaceae and Solanaceae species had less foreign pollen than expected, the ratios of pollen of recipient and donor respectively for both families were 80-20% and 60.5-39.5%. In contrast, Convolvulaceae species had just 28% recipient pollen and 72% of donor pollen. In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production. However, for just one species (*S. alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production. For two Solanaceae species *S. melongena* and *C. annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.

The grouped effect size of the nine donors per species differed across species and families (see **Figure 2**). Interestingly, despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**). Just for four species out of ten, just one donor in each did not overlap the confidence intervals with other donors. Therefore, none of the donors had a clear stronger or weaker effect across species. When the donors were grouped by family we found a similar effect too, just for *S. lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**).

@@

Caveats:
